Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-20 src/tex/ms.tex
Update ms.tex

\begin{abstract}
    One of the major problems that physicists are facing nowadays is Einstein's theory of general relativity does not agree with quantum theories at some length scales.
    In recent decades, theorist has been working on many beyond-GR theories to unify both of them.
    Some of these theories such as Chern-Simons gravity suggest that there is gravitational wave amplitude birefringence.
    In our study, we perform parameter estimation to constrain the strength of GW amplitude birefringence.
    Compare to similar previous studies on the same topic, we perform PE on more events, including events in the third LIGO-Virgo catalog, and we used a more accurate model of birefringence to describe the phenomenon.
    % results
\end{abstract}

>>>>

\begin{abstract}
    One of the major problems that physicists are facing nowadays is Einstein's theory of general relativity (GR) does not agree with quantum theories at some length scales.
    In recent decades, theorist has been working on many beyond-GR theories to unify both of them.
    Some of these theories such as Chern-Simons gravity suggest that there is gravitational wave (GW) amplitude birefringence.
    In our study, we perform parameter estimation (PE) to constrain the strength of GW amplitude birefringence.
    Compare to similar previous studies on the same topic, we perform PE on more events, including events in the third LIGO-Virgo catalog (GWTC-3), and we used a more accurate model of birefringence to describe the phenomenon.
    % results
\end{abstract}
